---
title: "Analysis"
author: "Jerry Dumblauskas"
date: "June 14, 2016"
output: html_document
---

From the coursera website:

"Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset)."


Training data at:
Test data at:

for this analysis we assume the data is downloaded and in the same directory.


```{r}
library(caret)
local_data_training <- read.csv('pml-training.csv')
local_data_testing <- read.csv('pml-testing.csv')
```

Set up a split on the training data
```{r}
set.seed(12345)
ts_in <- createDataPartition(y=local_data_training$classe, p=0.7, list=F)
ts_in1 <- local_data_training[ts_in, ]
ts_in2 <- local_data_training[-ts_in, ]

```

Clean up data
```{r}
# nzv (nearly zero)
nzv <- nearZeroVar(ts_in1)
ts_in1 <- ts_in1[, -nzv]
ts_in2 <- ts_in2[, -nzv]

# remove variables that are NA
l_NA <- sapply(ts_in1, function(x) mean(is.na(x))) > 0.96
ts_in1 <- ts_in1[, l_NA==F]
ts_in2 <- ts_in2[, l_NA==F]

# remove variables the first five variables (not needed for prediction)
ts_in1 <- ts_in1[, -(1:5)]
ts_in2 <- ts_in2[, -(1:5)]
```

Build the model.  Using Random Forest.  It takes awhile to run but seems to work well, and looks good on my resume :)
```{r}
# 3 fold cross validation
x_control <- trainControl(method="cv", number=3, verboseIter=F)

# fit da model
fit <- train(classe ~ ., data=ts_in1, method="rf", trControl=x_control)

print (fit$finalModel)
```

Get predicition and show confusion matrix
```{r}
# use model to predict classe in validation set (ts_in2)
preds <- predict(fit, newdata=ts_in2)

# show confusion matrix and get accuracy
confusionMatrix(ts_in2$classe, preds)

```
From the above, the accuracy is over 99% -- so this is good enough.


Predict on Test Set

```{r}
# predict on test set
preds <- predict(fit, newdata=local_data_testing)

print (preds)
```
